---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidyproj

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/almeidasilvaf/tidyproj/workflows/R-CMD-check/badge.svg)](https://github.com/almeidasilvaf/tidyproj/actions)
<!-- badges: end -->

The goal of `tidyproj` is to create a standard directory structure for scientific projects, including a code, data, and products directory. This way, all projects will look the same, making it easier to load and save data in different projects.

You can see an example directory created with `tidyproj` in inst/extdata. The directory structure looks like this:

```{r}
exampledir <- system.file("extdata", "exampledir", package = "tidyproj")
fs::dir_tree(exampledir)
```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("almeidasilvaf/tidyproj")
```

## Usage

Users can create the project structure with a single function:

```{r example, eval=FALSE}
library(tidyproj)
create_project_tree()
```
